A comparison of classification algorithms applied to the Adult Database

### 2009-12-10 report/final.tex
update best values

From tables \ref{tbl:results_adtree_discr} and \ref{tbl:results_adtree_raw}
we can see that the number of boosting iterations affects
both the execution time (directly proportional) and the error rate.
The best error rate for raw data is using the parameters \textbf{-E -1 -B 5} giving $\approx$18.58\% for the test set.

@@

\begin{table}
    \begin{center}
    \begin{tabular}{ | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    CN2 & 15.20 \\ \hline
    ID3 & 15.68 \\ \hline
    ADTree & 19.80 \\ \hline
    ILP (Aleph) & 20.45 \\ \hline
    Bayesian Networks (Simulated Annealing) & 21.09 \\ \hline
    C4.5 & 21.69 \\ \hline
    Random Forest & 22.71 \\ \hline
    Bayesian Networks (Hill Climbing) & 22.93 \\ \hline
    CART & 25.37 \\ \hline
    Bayesian Networks (Genetic Search) & - \\ \hline
    \end{tabular}
    \caption{Error rates for the different algorithms used in the classification process}
    \label{tbl:overall_results}
    \end{center}
\end{table}

>>>>

From tables \ref{tbl:results_adtree_discr} and \ref{tbl:results_adtree_raw}
we can see that the number of boosting iterations affects
both the execution time (directly proportional) and the error rate.
The best error rate for raw data is using the parameters \textbf{-E -3 -B 30} giving $\approx$18.49\% for the test set.

@@

\begin{table}
    \begin{center}
    \begin{tabular}{ | l | l | }
    \hline
    \textbf{Algorithm} & \textbf{Error rate} \\ \hline
    CN2 & 15.20 \\ \hline
    ID3 & 15.68 \\ \hline
    ADTree & 18.49 \\ \hline
    ILP (Aleph) & 20.45 \\ \hline
    Bayesian Networks (Simulated Annealing) & 21.09 \\ \hline
    C4.5 & 18.84 \\ \hline
    Random Forest & 22.71 \\ \hline
    Bayesian Networks (Hill Climbing) & 22.93 \\ \hline
    CART & 25.37 \\ \hline
    Bayesian Networks (Genetic Search) & - \\ \hline
    \end{tabular}
    \caption{Error rates for the different algorithms used in the classification process}
    \label{tbl:overall_results}
    \end{center}
\end{table}
